### 2020-02-02 article.tex
typo in Section 2.4 (experiments try) fixed

Since fMRI images are 3D time series and our experiment tries to find out if images contain any useful information despite their sequences, three dimensional CNN can be used as our computational core. A simple 3D CNN can be seen in Figure \ref{fig:CnnSample}.

>>>>

Since fMRI images are 3D time series and our experiments try to find out if images contain any useful information despite their sequences, three dimensional CNN can be used as our computational core. A simple 3D CNN can be seen in Figure \ref{fig:CnnSample}.
